Partitioning growth-dependent from growth-independent influences on tropical tree mortality

### 2018-08-22 ms/manuscript.Rnw
Added sentence just before results providing a little more context to the r2 and auroc statistics

Using a likelihood-based penalty for incorrect prediction, we used 10-fold cross-validation to evaluate the skill of different models in their ability to predict outcomes in novel data (i.e. not used in model fitting; Fig. \ref{fig1}C-D; see Methods) \cite{Hooten:2015, Stone:1997tg}. In total \Sexpr{n_obs(BCI_training_full)} observations were used to fit these models. Evaluating models in this way is computationally expensive. Therefore rather than running all possible model formulations, we fitted models across six levels of increasing complexity, described below, and comparing their predictive skill. We then use the final model to assess the effects of species traits on each parameter and quantify their relative contributions on the overall model performance.

>>>>

Using a likelihood-based penalty for incorrect prediction, we used 10-fold cross-validation to evaluate the skill of different models in their ability to predict outcomes in novel data (i.e. not used in model fitting; Fig. \ref{fig1}C-D; see Methods) \cite{Hooten:2015, Stone:1997tg}. In total \Sexpr{n_obs(BCI_training_full)} observations were used to fit these models. Evaluating models in this way is computationally expensive. Therefore rather than running all possible model formulations, we fitted models across six levels of increasing complexity, described below, and comparing their predictive skill. We then use the final model to assess the effects of species traits on each parameter and quantify their relative contributions on the overall model performance. Relative contributions of parameters were assessed using $r^2$ and Area Under the ROC Receiver Curve (AUROC). Whereby, $r^2$ estimates were derived from modelled predictions vs proportion of individual deaths observed between 1995 and 2010 for each species, and thus measured the amount of species-level variation explained by the model \cite{Visser_functional_2016}. By contrast, AUROC examined the model's ability to distinguish individuals that died from individuals that survived, irrespective of species.
